Methods to prioritise pop-up active transport infrastructure and their application in a national cycleway prioritisation tool

### 2020-06-22 article.Rmd
Update table

---
title: "Methods to prioritise pop-up active transport infrastructure and their application in a national cycleway prioritisation tool"
# : overview and findings from 10 UK cities"
author: "Robin Lovelace, Malcolm Morgan, Joey Talbot, Martin-Lucas-Smith"
output: bookdown::github_document2
# output: bookdown::html_document2
# output:
#   bookdown::pdf_document2:
#     keep_tex: true
# bibliography: references.bib
bibliography: refs.bib
---

@@

```{r, echo=FALSE, eval=FALSE}
citr::tidy_bib_file("article.Rmd", "~/uaf/allrefs.bib", file = "refs.bib")
wordcountaddin::word_count("article.Rmd")
knitr::purl("article.Rmd")
file.copy("article.R", "code/article-methods-1.R")
pagedown::chrome_print("article.html")
browseURL("article.pdf")
zf = list.files(pattern = "tex|png", full.names = TRUE)
zfl = list.files("article_files/figure-latex/", full.names = TRUE)
fz = c(zf, zfl)
msgf = paste(fz, collapse = " ")
msgf = gsub(pattern = "\\./", replacement = "", msgf)
msg = paste("tar -cvf article.tar ", msgf)
system(msg)
```

@@

```{r t1, results='asis', fig.cap="Summary of the road segment dataset for Leeds."}
# rj_leeds = readRDS("r_main_leeds.Rds")
# rj_leeds %>%
#   st_drop_geometry() %>% 
#   mutate(`width (m)` = width) %>% 
#   # select(name, highway_type, maxspeed, cycling_potential, width) %>% 
#   table1::table1(~ highway_type + cycling_potential + `width (m)` + n_lanes | maxspeed, data = ., )
# ut = "https://user-images.githubusercontent.com/1825120/81476961-c32d2500-920c-11ea-8430-94c3afc2e27d.png"
# knitr::include_graphics(ut)
# system(paste("wget ", ut))
knitr::include_graphics("figures/table1.png")
```

>>>>

---
title: "Methods to prioritise pop-up active transport infrastructure and their application in a national cycleway prioritisation tool"
# : overview and findings from 10 UK cities"
author: "Robin Lovelace, Malcolm Morgan, Joey Talbot, Martin-Lucas-Smith"
# output: bookdown::github_document2
# output: bookdown::html_document2
output:
  bookdown::pdf_document2:
    keep_tex: true
# bibliography: references.bib
bibliography: refs.bib
---

@@

```{r, echo=FALSE, eval=FALSE}
citr::tidy_bib_file("article.Rmd", "~/uaf/allrefs.bib", file = "refs.bib")
wordcountaddin::word_count("article.Rmd")
knitr::purl("article.Rmd")
file.copy("article.R", "code/article-methods-1.R")
pagedown::chrome_print("article.html")
browseURL("article.pdf")
zf = list.files(pattern = "tex|png", full.names = TRUE)
zfl = list.files("article_files/figure-latex/", full.names = TRUE)
fz = c(zf, zfl)
msgf = paste(fz, collapse = " ")
msgf = gsub(pattern = "\\./", replacement = "", msgf)
msg = paste("tar -cvf article.tar ", msgf)
system(msg)
install.packages("qwraps2")
install.packages("reporttools")
```

@@

```{r t1, results='asis', fig.cap="Summary of the road segment dataset for Leeds.", message=FALSE}
rj_leeds = readRDS("r_main_leeds.Rds")
# See https://cran.r-project.org/web/packages/qwraps2/vignettes/summary-statistics.html
# rj_leeds %>%
#   st_drop_geometry() %>%
#   mutate(`width (m)` = width) %>%
#   select(name, highway_type, maxspeed, cycling_potential, `width (m)`, n_lanes) %>%
#   group_by(maxspeed) %>% 
#   # qwraps2::summary_table()
#   table1::table1(~ highway_type + cycling_potential + `width (m)` + n_lanes | maxspeed, data = .)
t1 = readr::read_csv("input-data/t1.csv")[-1]
n = c(
  "N. observations",
  "(N=4777)",
  "(N=19241)",
  "(N=3105)",
  "(N=27123)"
)
names(n) = names(t1)
t2 = rbind(n, t1)
names(t2)[1] = ""
# t1
t2 %>% 
  kableExtra::kable(
    # escape = FALSE,
    booktabs = TRUE,
    # col.names = kableExtra::linebreak(names(t1)),
    format = "latex"
    ) %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::pack_rows("N. observations", 1, 2) %>% 
  kableExtra::pack_rows("Highway type", 2, 13) %>% 
  kableExtra::pack_rows("Cycling potential", 14, 15) %>%  
  kableExtra::pack_rows("Width (m)", 16, 18) %>% 
  kableExtra::pack_rows("N. lanes", 19, 22)

# ?kableExtra

# ut = "https://user-images.githubusercontent.com/1825120/81476961-c32d2500-920c-11ea-8430-94c3afc2e27d.png"
# knitr::include_graphics(ut)
# system(paste("wget ", ut))
# knitr::include_graphics("figures/table1.png")
```
